
% Lecture 9. Exercise Sessions
\subsubsection*{Risk Identification}
\textbf{1. Identify assets (e.g. web application)}
\begin{itemize}
    \item Web application
    \item Azure Database
    \item CircleCI Integration
    \item DigitalOcean Droplets
    \item GitHub Repository
    \item DockerHub Images
    \item Prometheus/Grafana
    \item ElasticSearch/Kibana
\end{itemize}
\textbf{2. Identify threat sources}\\
\vspace{5mm} %5mm vertical space
\textbf{Identification and authentication failures:} Public API does not check for any authentication and can change entities in the database. This means that you can access and create user tweets without being authenticated.
\vspace{5mm} %5mm vertical space
\\
\textbf{Software and Data Integrity Failures:} Our Backend written in C\# is never analysed during our pipeline deployment and therefore the not verifying integrity.
\vspace{5mm} %5mm vertical space
\\
\textbf{SQL Injection:} Through EF Core we automatically escape (sanitize) the user-inputs (users tweet message). This means that no user-input will be misinterpreted by our program after this point. As the user-input is not used in any logic or inserted anywhere before this point we find this approach adequate.
\vspace{5mm} %5mm vertical space
\\
\textbf{3. Construct risk scenarios}
\\
User uses the public API and sends requests to manipulate database without authentication.
\\
User sends too many request to our server (DDoS attack). The primary server will stop responding and the secondary server will take over and eventually stop responding as well.
\\
User gains access to a developer computer with User Secrets. This allows the User to access all our infrastructure.
\\
User locates a deprecated dependency with a security vulnerability and manipulate data or takes down infrastructure.
\subsubsection*{Risk Analysis}
\textbf{Determine likelihood}
\\
\textit{Missing API Auth}: Very High Frequency as this is a pretty apparent issue when using the API.\\
\textit{DDoS}: High Frequency. In recent years the amount of DDoS attacks has only increased according to Cloudflare\footnote{\url{https://blog.cloudflare.com/ddos-attack-trends-for-2021-q4/}}.\\
\textit{Dependency Vulnerability}: Medium Frequence. Dependencies are often updated to fix vulnerabilities and we must ensure that we are using the newest versions and do not use deprecated dependencies.\\
\textit{Access to Developer Device}: Very Low Frequency. Though this would give full access it would be password-protected and each individual infrastructure provider, like DigitalOcean, has its own account password (and for DigitalOcean also Two-Factor Authentication).\\
\textbf{Determine impact}\\
\textit{Missing API Auth}: This allows the user to tweet on others behalf which compromises all user authentication promises.\\
\textit{DDoS}: DDoS compromises availability but not data (compromising/leaking data) so it is not mission critical.\\
\textit{Dependency Vulnerability}: A potential vulnerability can result in partial or full data leak which in the real world can result in legal charges and fines. \\
\textit{Access to Developer Device}: Access to one of our devices can result in total shutdown of infrastructure and code deletion.\\
\textbf{Use a Risk Matrix to prioritize risk of scenarios}\\
\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{cllllll}
\cline{2-7}
\multicolumn{1}{c|}{}                                                                                & \multicolumn{1}{l|}{}                    & \multicolumn{1}{l|}{Very Low Severity}        & \multicolumn{1}{l|}{Low Severity}             & \multicolumn{1}{l|}{Medium Severity}          & \multicolumn{1}{l|}{High Severity}                & \multicolumn{1}{l|}{Very High Severity}                                                                          \\ \cline{2-7} 
\multicolumn{1}{c|}{}                                                                                & \multicolumn{1}{l|}{Very High Frequency} & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}} & \multicolumn{1}{l|}{\cellcolor[HTML]{FFCB2F}} & \multicolumn{1}{l|}{\cellcolor[HTML]{FD6864}}     & \multicolumn{1}{l|}{\cellcolor[HTML]{FD6864}{\color[HTML]{000000} Missing API Auth}}                             \\ \cline{2-7} 
\multicolumn{1}{c|}{}                                                                                & \multicolumn{1}{l|}{High Frequency}      & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}} & \multicolumn{1}{l|}{\cellcolor[HTML]{FFCB2F}} & \multicolumn{1}{l|}{\cellcolor[HTML]{FFCB2F}DDoS} & \multicolumn{1}{l|}{\cellcolor[HTML]{FD6864}}                                                                    \\ \cline{2-7} 
\multicolumn{1}{c|}{}                                                                                & \multicolumn{1}{l|}{Medium Frequency}    & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}} & \multicolumn{1}{l|}{\cellcolor[HTML]{FFCB2F}}     & \multicolumn{1}{l|}{\cellcolor[HTML]{FFCB2F}\begin{tabular}[c]{@{}l@{}}Dependency \\ Vulnerability\end{tabular}} \\ \cline{2-7} 
\multicolumn{1}{c|}{}                                                                                & \multicolumn{1}{l|}{Low Frequency}       & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}} & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}}     & \multicolumn{1}{l|}{\cellcolor[HTML]{F8FF00}}                                                                    \\ \cline{2-7} 
\multicolumn{1}{c|}{\multirow{-6}{*}{\begin{tabular}[c]{@{}c@{}}I\\ M\\ P\\ A\\ C\\ T\end{tabular}}} & \multicolumn{1}{l|}{Very Low Frequency}  & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}} & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}}     & \multicolumn{1}{l|}{\cellcolor[HTML]{2ECC71}Access to Developer Device}                                          \\ \cline{2-7} 
\multicolumn{7}{c}{PROBABILITY}
\end{tabular}%
}
\end{table}
\textbf{Discuss what are you going to do about each of the scenarios}\\
\textit{Missing API Auth}: With more course-time it would be very high priority to resolve this issue as it impacts user-data. This although is not a problem in our other API as these requests are authenticated through the website.\\
\textit{DDoS}: In situation with increased server-load it would make sense to enable DDoS-protection tools to reduce the risk of DDoS.\\
\textit{Dependency Vulnerability}: Dependabot\footnote{\url{https://github.com/dependabot}} can automatically notify us if any dependency needs to be updated.\\
\textit{Access to Developer Device}: We have ensured that all developer devices are password-protect and that all DigitalOcean users with access to our infrastructure is protected by Two-Factor Authentication.